### 2011-07-07 docs/visualization/visualization.tex
add list of plotfiles

\section{Visualizing with \amrvis}
\section{Visualizing with \visit}
\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at {\tt http://yt.enzotools.org/}.

>>>>

\section{Plotfiles}

\maestro\ outputs plotfile specifically for visualization and analysis.
Table~\ref{vis:table:plotfile} lists the quantities stored in a plotfile.
Not all of these may be present, dependent on what options were used in 
creating the plotfile.

By default, plotfiles store double precision data, but if {\tt
  single\_prec\_plotfiles = .true.} is set, then the data is converted
to single precision before outputting---this is done to reduce file
sizes.

\renewcommand{\arraystretch}{1.3}

\begin{center}
\begin{longtable}{|l|p{2.25in}|p{2.5in}|}
\caption{Plotfile quantities}
\label{vis:table:plotfile} \\
%
\hline \multicolumn{1}{|c|}{\textbf{plotfile variable name}} & 
       \multicolumn{1}{|c|}{\textbf{description}} & 
       \multicolumn{1}{|c|}{\textbf{runtime parameter controlling output}} \\ \hline
\endfirsthead

\multicolumn{3}{c}%          
{{\tablename\ \thetable{}---continued}} \\
\hline {plotfile variable name} & 
       {description} & 
       {runtime parameter controlling output} \\ \hline
\endhead

\multicolumn{3}{|r|}{{\em continued on next page}} \\ \hline
\endfoot

\hline
\endlastfoot

{\tt x\_vel}   & $\ut$  & -- \\
\hline
{\tt y\_vel}   & $\vt$  & -- \\
\hline
{\tt z\_vel}   & $\wt$  & 3-d runs online \\
\hline
{\tt density}  & $\rho$ & -- \\
\hline
{\tt rhoh}   & $(\rho h)$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           
\hline
{\tt h}      & $(\rho h)/\rho$   & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           
\hline
{\tt X(*)}   & $(\rho X_k)/\rho$ & {\tt plot\_spec} \\
\hline
{\tt tracer} & tracers           & {\tt plot\_trac} \\
\hline
{\tt w0\_x}  & $w_0 \er \cdot \ex$ & {\tt plot\_base} \\ 
\hline
{\tt w0\_y}  & $w_0 \er \cdot \ey$ & {\tt plot\_base} \\ 
\hline
{\tt w0\_z}  & $w_0 \er \cdot \ez$ & {\tt plot\_base} \\ 
\hline
{\tt divw0}  & $\nabla \cdot w_0$  & {\tt plot\_base} \\ 
\hline
{\tt rho0}   & $\rho_0$            & {\tt plot\_base} \\ 
\hline
{\tt rhoh0}  & $(\rho h)_0$         & {\tt plot\_base} \\ 
\hline
{\tt h0}     & $(\rho h)_0/\rho_0$  & {\tt plot\_base} \\ 
\hline
{\tt p0}     & $p_0$                & {\tt plot\_base} \\ 
\hline
{\tt radial\_velocity}  & $\Ubt \cdot \er + w_0$ & {\tt spherical == 1} \\
\hline
{\tt circum\_velocity}  & $| \Ubt - (\Ubt \cdot \er) \er |$ &  {\tt spherical == 1}  \\
\hline
{\tt magvel}              & $| \Ubt + w_0 \er |$  & -- \\
\hline
{\tt momentum}            & $\rho | \Ubt + w_0 \er |$  & -- \\
\hline
{\tt vort}                & $| \nabla \times \Ubt |$   & -- \\
\hline
{\tt S}                   & $S$   & -- \\
\hline
{\tt rhopert}             & $\rho - \rho_0$  & -- \\
\hline
{\tt rhohpert}          & $(\rho h) - (\rho h)_0$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           
\hline
{\tt tfromp}              & $T(\rho, p_0, X_k)$  & -- \\
\hline
{\tt tfromh}            & $T(\rho, h, X_k)$    & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           
\hline
{\tt deltaT}            & $[T(\rho, h, X_k) - T(\rho, p_0, X_k)]/T(\rho, h, X_k)$  & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           
\hline
{\tt deltap}            & $|p(\rho,h,X_k) - p_0|/p_0$ & {\tt use\_tfromp = F} or ({\tt use\_tfromp = T} amd {\tt plot\_h\_with\_use\_tfromp = T}) \\           
\hline
{\tt tpert}               & $T(\rho,h,X_k) - \overline{T}$ if {\tt use\_tfromp = F}; $T(\rho,p_0,X_k) - \overline{T}$ otherwise & -- \\
\hline
{\tt Machnumber}          & $| \Ubt + w_0 \er | / c(\rho,p_0,X_k)$ & -- \\
\hline
{\tt soundspeed}        & $c(\rho,p_0,X_k)$ & {\tt plot\_cs} \\
\hline
{\tt deltagamma}          & $\Gamma_1(\rho,p_0,X_k) - \gammabar$ & -- \\
\hline
{\tt entropy}             & $s(\rho,p_0,X_k)$ & -- \\
\hline
{\tt entropypert}         & $[s(\rho,p_0,X_k) - \overline{s}]/\overline{s}$ & -- \\
\hline
{\tt sponge} or {\tt sponge\_fdamp} & $1/(1 + \Delta t \kappa f_\mathrm{damp})$ by default; $f_\mathrm{damp}$ if {\tt plot\_sponge\_fdamp = T} & -- \\
\hline
{\tt pi}                 & $\pi$ & -- \\
\hline
{\tt gpi\_x}           & $\nabla \pi \cdot \ex$ & {\tt plot\_gpi} \\
\hline 
{\tt gpi\_y}           & $\nabla \pi \cdot \ey$ & {\tt plot\_gpi} \\
\hline
{\tt gpi\_z}           & $\nabla \pi \cdot \ez$ & {\tt plot\_gpi} \\
\hline
{\tt pioverp0}         & $\pi / p_0$ & {\tt plot\_base} \\
\hline
{\tt p0pluspi}         & $p_0 + \pi$ & {\tt plot\_base} \\
\hline
{\tt omegadot(*)}      & $(\rho X_k)/\rho$ & {\tt plot\_omegadot} \\
\hline
{\tt enucdot}          & $(\rho \Hnuc)/\rho$ & {\tt plot\_Hnuc} \\
\hline
{\tt Hext}             & $(\rho \Hext)/\rho$ & {\tt plot\_Hext} \\
\hline
{\tt eta\_rho}         & $\etarho$ & {\tt plot\_eta} \\
\hline
{\tt thermal}          & $\nabla \cdot \kappa \nabla T$ & {\tt use\_thermal\_diffusion} \\
\hline
{\tt conductivity}     & $\kappa(\rho, T, X_k)$ & {\tt use\_thermal\_diffusion} \\
\hline
{\tt ad\_excess}       & $\nabla - \nabla_\mathrm{ad}$ & {\tt plot\_ad\_excess} \\
\hline
\end{longtable}
\end{center}

\renewcommand{\arraystretch}{1.0}

\section{Visualizing with \amrvis}

\section{Visualizing with \visit}

\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at {\tt http://yt.enzotools.org/}.
